### 2022-12-28 paper.tex
INIT: Initial template

% ---------------------------------------------------------------------------
% Author guideline and sample document for EG publication using LaTeX2e input
% D.Fellner, v1.13, Nov 13, 2007

\documentclass{egpubl}

% --- for  Annual CONFERENCE
\VisualComputing % VisualComputing (added by U. Schwanecke, 2021)
%\ThreeDAnimation % 3DAnimation (added by U. Schwanecke, 2020)
%\Seminar % Specialist Seminar (added by U. Schwanecke, 2019)
%\ConferenceSubmission % uncomment for Conference submission
%\ConferencePaper      % uncomment for (final) Conference Paper
%\STAR                 % uncomment for STAR contribution
% \Tutorial             % uncomment for Tutorial contribution
% \ShortPresentation    % uncomment for (final) Short Conference Presentation
%
% --- for  CGF Journal
% \JournalSubmission    % uncomment for submission to Computer Graphics Forum
% \JournalPaper         % uncomment for final version of Journal Paper
%
% --- for  CGF Journal: special issue
% \SpecialIssueSubmission    % uncomment for submission to Computer Graphics Forum, special issue
% \SpecialIssuePaper         % uncomment for final version of Journal Paper, special issue
%
% --- for  EG Workshop Proceedings
% \WsSubmission    % uncomment for submission to EG Workshop
% \WsPaper         % uncomment for final version of EG Workshop contribution
%
%\electronicVersion % can be used both for the printed and electronic version

% !! *please* don't change anything above
% !! unless you REALLY know what you are doing
% ------------------------------------------------------------------------

\PrintedOrElectronic

\usepackage[pdftex]{graphicx} 
\usepackage{t1enc, dfadobe}
%\usepackage[T1]{fontenc}
\usepackage{egweblnk}
\usepackage{cite}

% For backwards compatibility to old LaTeX type font selection.
% Uncomment if your document adheres to LaTeX2e recommendations.
% \let\rm=\rmfamily    \let\sf=\sffamily    \let\tt=\ttfamily
% \let\it=\itshape     \let\sl=\slshape     \let\sc=\scshape
% \let\bf=\bfseries

% end of prologue

\usepackage{blindtext}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{dblfloatfix}
\usepackage{adjustbox}
\usepackage{mathtools}
\usepackage{todonotes}

% ---------------------------------------------------------------------
\captionsetup{labelfont=bf,textfont=it}
\title[Fancy 3D Animation Demo]%
      {Fancy Paper in the Field of Visual Computing}

\author[U. Schwanecke]
    {\parbox{\textwidth}
        {\centering 
			U. Schwanecke
        }
        \\
    {\parbox{\textwidth}
        {\centering RheinMain University of Applied Sciences, Wiesbaden, Germany\\
       }
    }
}
% ------------------------------------------------------------------------

% if the Editors-in-Chief have given you the data, you may uncomment
% the following five lines and insert it here
%
% \volume{36}   % the volume in which the issue will be published;
% \issue{1}     % the issue number of the publication
% \pStartPage{1}      % set starting page

%-------------------------------------------------------------------------
\begin{document}

%-------------------------------------------------------------------------
% uncomment for using teaser (comment if you don't want a teaser)
\teaser{
    \hspace{\fill}
    \includegraphics[width=0.9\linewidth]{images/ModelbasedTrackingExample.png}
    \hspace{\fill}
    \centering
    \caption{Best teaser image you can provide \ldots}
    \label{fig:teaser}
}

%-------------------------------------------------------------------------
\maketitle

%-------------------------------------------------------------------------
\begin{abstract}
Some informative abstract \ldots
\blindtext
\end{abstract}

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}
Some nice introduction, e.g. citing some literature such as \cite{Tjaden2017, Achenbach2018, Sommer2020} \ldots

$$
\sum_{i=1}^n i = \frac{n(n+1)}{2}
$$
\blindtext

%-------------------------------------------------------------------------
\section{Related Work}
\label{sec:related_work}
Maybe a separate section about related work \ldots 
\blindtext

%-------------------------------------------------------------------------
\section{Approach}
\label{sec:approach}
\blindtext

%-------------------------------------------------------------------------
\section{Experiments}
\label{sec:Experiments}
\blindtext

%-------------------------------------------------------------------------
\section{Conclusions}
\label{sec:conclusion}
Some famous last words \ldots
\blindtext

%-------------------------------------------------------------------------
\section{Acknowledgements}
\label{sec:acknowledgements}
Maybe you like to acknowledge \ldots

%-------------------------------------------------------------------------
%\bibliographystyle{eg-alpha}
\bibliographystyle{eg-alpha-doi}
\bibliography{paper-bib}

\end{document}

### 2022-12-28 paper.tex
REFACTOR: Adjust semester, author and title
REFACTOR: Adjust introduction and references

@@
 \captionsetup{labelfont=bf,textfont=it}
-\title[Fancy 3D Animation Demo]%
-      {Fancy Paper in the Field of Visual Computing}
+\title[Burst Images]%
+      {Burst Images}
 
-\author[U. Schwanecke]
+\author[Sascha Scheid]
     {\parbox{\textwidth}
         {\centering 
-			U. Schwanecke
+			Sascha Scheid
         }
@@
 \label{sec:introduction}
-Some nice introduction, e.g. citing some literature such as \cite{Tjaden2017, Achenbach2018, Sommer2020} \ldots
 
-$$
-\sum_{i=1}^n i = \frac{n(n+1)}{2}
-$$
-\blindtext
+Burst photography is a technique in which a series of photographs is taken quickly in succession.
+This can be useful in a variety of situations, such as capturing action or movement, 
+or to create a sense of motion. In digital photography, burst images are stored as a 
+sequence of image files, typically in a format such as JPEG or RAW.
+
+High Dynamic Range (HDR) is a technique used to improve the dynamic range of an image, 
+which is the range of luminance or brightness levels that can be captured in a photograph. 
+The dynamic range of a scene can often be greater than what a camera is able to capture 
+in a single image, resulting in lost detail in the highlights or shadows. 
+HDR techniques can be used to extend the range of luminance in an image, 
+resulting in more detail and a more realistic representation of the scene.
+
+One way that burst photography and HDR techniques can be used together in mobile cameras 
+is to capture a series of photographs with different exposures in a burst, and then combine 
+the exposures into a single HDR image using software. This can be particularly useful in 
+low-light situations, where the camera may struggle to capture a wide range of luminance 
+levels in a single exposure. By capturing multiple exposures and combining them into an 
+HDR image, it is possible to extend the dynamic range and capture more detail in both the 
+highlights and shadows.
+
+\cite{Hasinoff2016Burst}
 

### 2022-12-31 documentation/paper.tex
REFACTOR: Add hdrplus implementation provided by Dockerfile

--- 2022-12-28 paper.tex
@@
 
-One way that burst photography and HDR techniques can be used together in mobile cameras 
+One way that burst photography and HDR techniques can be used together
 is to capture a series of photographs with different exposures in a burst, and then combine 

### 2023-01-01 documentation/paper.tex
FEATURE: Add section for approach and experiments

@@
 
-\cite{Hasinoff2016Burst}
-
 %-------------------------------------------------------------------------
@@
 \label{sec:approach}
-\blindtext
+
+The classic manual approach from digital photography is to take three images of the same scene: 
+One overexposed, one underexposed, and one normally exposed. These are superimposed in 
+post-processing so that the bright areas of the resulting image are not too bright and the 
+dark areas are not too dark. This results in an image that not only contains many bright areas, 
+but also many dark areas at the same time.
+
+This classical approach will be contrasted with the method described in \ref{sec:related_work}. 
+For this purpose, image bursts of the same scene are processed once according to the 
+classical method and once according to the method described in \ref{sec:related_work}. To get a good 
+comparison, images of stationary and moving objects are taken, both from a tripod and 
+handheld.
 
@@
 \label{sec:Experiments}
-\blindtext
+\cite{Brooks2016git} has implemented the image processing pipeline described in \ref*{sec:related_work}. To do this, 
+he uses Halide, a programming language embedded in C++ that allows efficient image processing 
+pipelines to be implemented with little effort. Halide itself requires LLVM to compile. 
+Unfortunately, the project has not been actively maintained for quite some time and 
+since new versions of Halide and LLVM have been released in the meantime, some of which were 
+not backwards compatible, the project could not be compiled out of the box. After many hours of 
+trial and error, the project was able to compile with version 10 of both Halide and LLVM. 
+To get a reproducible executable version of \cite{Brooks2016git}, a Docker image was created that 
+contains the application and runs it on container startup.
 

### 2023-01-01 hdrplus-implementation/resources/process.sh
FEATURE: Enable parallel processing of multiple image bursts

@@ -1,0 +1,45 @@
+#!/usr/bin/bash
+
+###########################################################
+#                                                         #
+# Author: Sascha Scheid                                   #
+# Date:   2023-01-01                                      #
+#                                                         #
+# This script triggers execution of the hdrplus program   #
+# to process multiple image bursts in parallel.           #
+#                                                         #
+###########################################################
+
+if [ ! -f /.dockerenv ] || [ ! -f /hdr-plus/hdrplus ]
+then
+    echo "This script is meant to run inside a container where hdrplus is present."
+    echo "Standalone execution is not possible"
+    exit 1
+fi
+
+INPUT_DIR=/bursts
+OUTFILE=output.jpg
+
+# Enable extended globbing to be able to only 
+# use RAW files as arguments for hdrplus 
+shopt -s extglob
+
+# Start a hdrplus process for every burst directory.
+# This enables processing multiple bursts in parallel.
+for burstdir in "$INPUT_DIR"/*
+do
+    # Ignore burst directories that have already been processed
+    if [ -d "$burstdir" ] && [ ! -f "$burstdir/$OUTFILE" ]
+    then
+        logfile="$burstdir/$(date '+%F_%T').log"
+        ./hdr-plus/hdrplus "." "$burstdir/$OUTFILE" "$burstdir"/@(*.RAW|*.raw|*.ARW|*.arw|*.DNG|*.dng) > "$logfile" 2>&1 &
+    fi
+done
+
+# Disable extended globbing
+shopt -u extglob
+
+# Wait for all jobs to finish.
+# Without this the Docker container will
+# shutdown after starting all jobs.
+wait

### 2023-01-02 hdrplus-implementation/resources/process.sh
REFACTOR: Adjust output filename to .png instead of .jpg. Add clean command to remove all output files

@@ -18,7 +18,7 @@ then
 fi
 
 INPUT_DIR=/bursts
-OUTFILE=output.jpg
+OUTFILE=output.png
 
 # Enable extended globbing to be able to only 
 # use RAW files as arguments for hdrplus 

### 2023-01-02 hdrplus-implementation/resources/process.sh
FEATURE: Enable individual flags for each burst via config file

@@ -31,8 +31,24 @@ do
     # Ignore burst directories that have already been processed
     if [ -d "$burstdir" ] && [ ! -f "$burstdir/$OUTFILE" ]
     then
-        logfile="$burstdir/$(date '+%F_%T').log"
-        ./hdr-plus/hdrplus "." "$burstdir/$OUTFILE" "$burstdir"/@(*.RAW|*.raw|*.ARW|*.arw|*.DNG|*.dng) > "$logfile" 2>&1 &
+
+        logdir="$burstdir/logs"
+        logfile="$logdir/$(date '+%F_%T').log"
+        configfile="$burstdir/hdrplus.config"
+    
+        # Ensure log directory exists (modify permissions to be able to delete it from without the container!)
+        [ -d "$logdir" ] || mkdir "$logdir" && chmod 0777 "$logdir"
+
+        flags=""
+
+        # Set flags according to configuration file if present
+        if [ -f "$configfile" ]
+        then
+            cat "$configfile" >> "$logfile"
+            eval $(cat "$configfile" | xargs)
+            [ ! -z ${GAIN+x} ] && flags="$flags -g $GAIN" && [ ! -z ${COMPRESSION+x} ] && flags="$flags -c $COMPRESSION"
+        fi
+        ./hdr-plus/hdrplus $flags "." "$burstdir/$OUTFILE" "$burstdir"/@(*.RAW|*.raw|*.ARW|*.arw|*.DNG|*.dng) >> "$logfile" 2>&1 &
     fi
 done
 

### 2023-01-19 documentation/paper.tex
FEATURE: Add text and bullet points

--- 2022-12-31 documentation/paper.tex
@@
 \usepackage{todonotes}
+
+\usepackage{cleveref}
 
@@
 
-\cite{Hasinoff2016Burst}
+Mobile cameras can have several constraints in low light situations, including:
+
+\begin{itemize}
+    \item Low sensitivity: Mobile cameras often have smaller sensors compared 
+          to DSLR or mirrorless cameras, which can result in lower sensitivity 
+          to light. This can make it difficult to capture usable images in low l
+          ight conditions without using long exposures or high ISO values, 
+          which can introduce noise and other artifacts.
+
+    \item Limited dynamic range: Mobile cameras can have limited dynamic range, 
+          which can make it difficult to capture both the shadow and highlight 
+          details in a scene. This can result in underexposed or overexposed 
+          areas in the image, and can be particularly challenging in low light 
+          conditions where the range of luminance values is often greater.
+
+    \item Motion blur: Long exposures are often necessary in low light conditions, 
+          which can result in motion blur if the camera or the subject is moving. 
+          This can be particularly problematic for handheld shots or when photographing 
+          moving subjects.
+\end{itemize}
+
+To address these constraints, several techniques can be used to improve the performance 
+of mobile cameras in low light conditions. These include:
+
+\begin{itemize}
+    \item Noise reduction: Noise reduction algorithms can be used to reduce the noise 
+          introduced by high ISO values or long exposures. These algorithms can smooth 
+          out the image while preserving edges and other important details.
+
+    \item High dynamic range techniques: HDR techniques, such as burst photography 
+          and computational photography, can be used to extend the dynamic range of mobile 
+          cameras and capture more detail in both the shadow and highlight areas of an image.
+
+    \item Image stabilization: Image stabilization technologies, such as optical image 
+          stabilization or electronic image stabilization, can be used to reduce the 
+          effects of camera shake or subject movement during long exposures.
+\end{itemize}
+
+While there are still limitations to the capabilities of mobile cameras compared to larger, 
+more specialized cameras, advances in technology and image processing algorithms are 
+continually improving the quality and performance of mobile cameras in a variety of 
+lighting conditions.
 
@@
 \label{sec:related_work}
-Maybe a separate section about related work \ldots 
-\blindtext
+
+The HDR+ algorithm is a computational photography technique developed by Google for use 
+in the Google Pixel smartphone. It is designed to capture high dynamic range images using 
+burst photography. The algorithm uses computational techniques to extend the dynamic range 
+of the captured images, rather than relying on multiple exposures as in traditional 
+HDR techniques, in which a rapid sequence of images at different exposures is captured.
+The captured images are merged to create a single HDR image. The HDR+ algorithm was developed 
+to improve the quality and dynamic range of images captured on mobile devices, particularly in 
+low-light conditions. The HDR+ algorithm consists of several steps, which are outlined in detail 
+in \cite{Hasinoff2016burst}. In brief, the steps are as follows:
+
+\begin{enumerate}
+    \item Burst capture: A sequence of raw images is captured. In contrast to the classic 
+          multi-exposure approach, each image will be underexposed and all images have the
+          same exposure. An image bursts consists of two to eight single images.
+    \item Image alignment: The sharpest image of the first three images in the burst is 
+          selected as reference image and the remaining images in the burst are aligned 
+          to it. This corrects for any movement or misalignment between frames.
+    \item Image merging: The aligned raw images are merged to create a single intermediate 
+          raw image that will then be further processed.
+    \item Finishing: The merged image undergoes a set of operations including general
+          correction, demosaicking and tone mapping. The most important operation is
+          dynamic range compression which reduces the contrast between light and dark
+          areas while preserving local contrast. To do so, the local tone mapping method
+          \textit{exposure fusion} was used, which blends together the best parts of
+          differently exposed images. As there is only one merged image left, the ones 
+          to blend are created synthetically from the merged image.
+
+\end{enumerate}
 
@@
 \label{sec:approach}
-\blindtext
+
+\begin{itemize}
+      \item Provide more details
+      \begin{itemize}
+            \item why does the git project not work?
+            \item overall architecture
+            \item how does the script work?
+            \item folder structure
+            \item configuration
+      \end{itemize}
+\end{itemize}
+
+\cite{Brooks2016git} has implemented the image processing pipeline described in \cref{sec:related_work}. To do this, 
+he uses Halide, a programming language embedded in C++ that allows efficient image processing 
+pipelines to be implemented with little effort. Halide itself requires LLVM to compile. 
+Unfortunately, the project has not been actively maintained for quite some time and 
+since new versions of Halide and LLVM have been released in the meantime, some of which were 
+not backwards compatible, the project could not be compiled out of the box. After many hours of 
+trial and error, the project was able to compile with version 10 of both Halide and LLVM. 
+To get a reproducible executable version of \cite{Brooks2016git}, a Docker image was created that 
+contains the application and runs it on container startup. To improve efficiency, a script was created 
+that starts processing all image bursts that are stored inside a bursts directory, which is shared
+with the Docker container, in parallel. \Cref{fig:architecture} shows the architecture described above.
+
+\begin{figure}
+    \hspace{\fill}
+    \includegraphics[width=0.9\linewidth]{images/architecture.png}
+    \hspace{\fill}
+    \centering
+    \caption{Architecture of the dockerized application}
+    \label{fig:architecture}
+\end{figure}
 
@@
 \label{sec:Experiments}
-\blindtext
+
+\begin{itemize}
+      \item Insert images
+      \item Compare raw vs processed
+      \item Show examples for scenarios:
+      \begin{itemize}
+            \item Low light noise reduction
+            \item Improving contrast / dynamic range
+            \item Improving overall colors
+      \end{itemize}
+      \item Show fails
+\end{itemize}
 
@@
 \section{Conclusions}
+
+\begin{itemize}
+      \item Are there scenes that are very easy or hard to improve?
+      \item Advantages:
+      \begin{itemize}
+            \item (Revived dead open source project, yay)
+            \item Portable solution because Docker
+            \item Parallel processing of multiple bursts
+            \item Not as much work as manually editing bracketed bursts in photoshop
+      \end{itemize}
+      \item Drawbacks:
+      \begin{itemize}
+            \item Long initial compiling time when building Docker image
+            \item Overhead because Docker
+            \item Ease of use: command-line only, adjusting config by editing a file
+      \end{itemize}
+      \item Future:
+      \begin{itemize}
+            \item Use case: Photographer wanting HDR images, but does not want to spend
+                  hours in photoshop
+            \item Providing GUI:
+            \begin{itemize}
+                  \item Hide docker and script execution for non-nerdy users
+                  \item Select burst folders to processes
+                  \item Adjust gain and compress parameters by slider per folder
+                  \item Start processing of selected folders via button click
+                  \item Show result images when finished
+            \end{itemize}
+      \end{itemize}
+\end{itemize}
 \label{sec:conclusion}
-Some famous last words \ldots
-\blindtext
 
@@
 \label{sec:acknowledgements}
-Maybe you like to acknowledge \ldots
+\begin{itemize}
+      \item Cat
+      \item Elementary school teacher
+      \item Ex girlfriend
+      \item Random dude at the bar who bought a round
+\end{itemize}
 

### 2023-01-26 documentation/paper.tex
FEATURE: Add images

@@
     \hspace{\fill}
-    \includegraphics[width=0.9\linewidth]{images/ModelbasedTrackingExample.png}
+    \includegraphics[width=0.9\linewidth]{images/teaser.png}
     \hspace{\fill}
     \centering
-    \caption{Best teaser image you can provide \ldots}
+    \caption{
+      Left images: Sample from a image burst captured with a Sony Alpha A6000 camera
+                   with focal length $18mm$, shutter speed $1/50s$, ISO $400$ 
+                   and aperture $f/4.0$ in a low light situation.
+      Right image: Processed burst images with settings gain $g = 1.2$ and dynamic 
+                   range compression $c = 3.0$.
+    }
     \label{fig:teaser}
@@
           multi-exposure approach, each image will be underexposed and all images have the
-          same exposure. An image bursts consists of two to eight single images.
+          same exposure. An image burst consists of two to eight single images.
     \item Image alignment: The sharpest image of the first three images in the burst is 
@@
           to blend are created synthetically from the merged image.
-
 \end{enumerate}
@@
 
+\subsection{Noisy low light situations}
+
+\begin{figure}
+      \hspace{\fill}
+      \includegraphics[width=0.9\linewidth]{images/noise.png}
+      \hspace{\fill}
+      \centering
+      \caption{
+            Left images: Noisy low light sample from bursts provided by the supplemental dataset
+            to \cite{Hasinoff2016burst}. Top row shows full image while bottom shows zoom in noisy
+            area.
+            Right images: Processed burst images with settings gain $g=1.0$ and dynamic 
+            range compression $c=2.5$.
+      }
+      \label{fig:noise}
+\end{figure}
+
+To find out how the HDR+ implementation handles images containing high noise, several 
+image bursts with high noise were processed. As can be seen in \cref{fig:noise}, the noise was 
+removed very well in all examples. Even when zooming in, hardly any noise is visible 
+compared to the original image.  The results were all obtained with the same starting 
+parameters and were satisfactory throughout.
+
+\subsection{Low contrast or dynamic range situations}
+
+\begin{figure}
+      \hspace{\fill}
+      \includegraphics[width=0.9\linewidth]{images/contrast_burst.png}
+      \hspace{\fill}
+      \centering
+      \caption{
+            Left images: Low contrast sample from bursts provided by the supplemental dataset
+            to \cite{Hasinoff2016burst}.
+            Right images: Processed burst images with settings gain g and dynamic 
+            range compression c from top to bottom image: $g=1.0$, $c=2.5$ | $g=1.0$, $c=1.5$ | $g=1.0$, $c=1.5$.
+      }
+      \label{fig:contrast}
+\end{figure}
+
+\cref{fig:contrast}
+
+\subsection{Moving objects}
+
+\begin{figure*}
+      \hspace{\fill}
+      \includegraphics[width=0.9\linewidth]{images/moving_burst.png}
+      \hspace{\fill}
+      \centering
+      \caption{Low light image capture of moving objects}
+      \label{fig:moving}
+\end{figure*}
+
+\begin{figure}
+      \hspace{\fill}
+      \includegraphics[width=0.9\linewidth]{images/ghosting.png}
+      \hspace{\fill}
+      \centering
+      \caption{Detail of \cref{fig:moving} showing ghosting }
+      \label{fig:ghosting}
+\end{figure}
+
+\cref{fig:moving}
+\cref{fig:ghosting}
+
 %-------------------------------------------------------------------------
@@
       \item Cat
-      \item Elementary school teacher
-      \item Ex girlfriend
+      \item Elementary school teacher5
       \item Random dude at the bar who bought a round

### 2023-02-09 documentation/paper.tex
Finish

@@
                    and aperture $f/4.0$ in a low light situation.
-      Right image: Processed burst images with settings gain $g = 1.2$ and dynamic 
+      Right image: Processed image burst with settings gain $g = 1.2$ and dynamic 
                    range compression $c = 3.0$.
@@
 \begin{abstract}
-Some informative abstract \ldots
-\blindtext
+Compared to cameras built specifically for photography, cameras used in smartphones 
+suffer from constructional limitations that restrict image quality, such as smaller 
+sensors and pixels, shorter focal lengths and smaller apertures. To compensate for 
+these limitations, techniques from computational photography are used, whereby many 
+current improvements are based on the processing of several similar images of the same 
+scene - so-called image bursts. In the course of this work, an existing implementation 
+of a burst processing pipeline was examined more closely and applied to example bursts 
+from mobile and DSLR cameras. In order to enable as many people as possible to 
+experiment with this implementation, it was adapted in such a way that it can be 
+used platform-independently. Even if performance and operation are not sufficient 
+to be used in a business context, it is suitable for an introduction to and initial 
+experimentation with burst processing.
 \end{abstract}
@@
 is to capture a series of photographs with different exposures in a burst, and then combine 
-the exposures into a single HDR image using software. This can be particularly useful in 
-low-light situations, where the camera may struggle to capture a wide range of luminance 
-levels in a single exposure. By capturing multiple exposures and combining them into an 
+the exposures into a single HDR image using software. This technique is known as 
+\textit{exposure bracketing} and is described by Mann {\&} Picard (2019) \cite{mann1994bracketing}. 
+This can be particularly useful in low-light situations, where the camera may struggle to 
+capture a wide range of luminance levels in a single exposure. By capturing multiple exposures and combining them into an 
 HDR image, it is possible to extend the dynamic range and capture more detail in both the 
@@
 
-Mobile cameras can have several constraints in low light situations, including:
+According to the photo sharing community Flickr, the most 
+popular cameras among users are those built into mobile phones \cite{flickr2023popularity}. Unlike dedicated photo cameras, these have 
+some inherent disadvantages which are outlined by Delbracio et al. (2021) \cite{delbracio2021mobile}. 
+They include:
 
@@
           which can introduce noise and other artifacts.
+
+    \item Limited zooming capability: Due to its small form factor, it is difficult to mount a lens 
+          with a highly variable focal length in front of the sensor of a cell phone.
+          Thus, they have to heavily rely on digital zoom instead of optical zoom which can lead to loss 
+          in sharpness of the zoomed in image.
 
@@
 
-The HDR+ algorithm is a computational photography technique developed by Google for use 
+The HDR+ image processing pipeline is a computational photography technique developed by Google for use 
 in the Google Pixel smartphone. It is designed to capture high dynamic range images using 
@@
 low-light conditions. The HDR+ algorithm consists of several steps, which are outlined in detail 
-in \cite{Hasinoff2016burst}. In brief, the steps are as follows:
+by Hasinoff et al. (2016) \cite{Hasinoff2016burst}. In brief, the steps are as follows:
 
@@
           areas while preserving local contrast. To do so, the local tone mapping method
-          \textit{exposure fusion} was used, which blends together the best parts of
-          differently exposed images. As there is only one merged image left, the ones 
-          to blend are created synthetically from the merged image.
+          \textit{exposure fusion} described by Mertens et al. (2007) \cite{mertens2007exposure} 
+          was used, which blends together the best parts of differently exposed images. 
+          As there is only one merged image left after step 3, the ones to blend are created synthetically 
+          from the merged image.
 \end{enumerate}
+
+To increase the amount of light collected, Levoy {\&} Pritch (2018) \cite{levoy2018psl} describe 
+the positive shutter lag recording technique, which, unlike zero shutter lag, does not 
+continuously capture frames of the scene in a ring buffer, but only after the shutter button is pressed,
+which allows longer exposures of the scene. However, this recording technique is more susceptible to motion blur.
+This problem was addressed by Liba et al. (2019) \cite{liba2019handheld} who further improved the HDR+ 
+pipeline by collecting real-time motion data before the shutter button is pressed. Based on this data, the motion 
+during the shot is predicted and an appropriate exposure duration is selected. In addition, 
+they use a learning-based approach for auto-white balancing, which has been specially trained 
+for night situations.
+
+Wronski et al. (2019) \cite{Wronski2019superres} describe a super-resolution based image processing pipeline that 
+is based on burst image processing pipelines like HDR+. It utilizes the inherent micro movement of hands while
+taking pictures with a mobile device to capture multiple frames of a scene with minimal offsets. Unlike other
+image processing pipelines, their approach does not include explicit demosaicking.
+
+An approach to image burst processing based only on neural networks was developed by Dudhane et al. (2022)
+\cite{Dudhane2022restoration}. They create a set of synthetic burst features by combining information of the
+captured images and afterwards merge them in multiple steps while increasing resolution continuously.
 
@@
 
-\begin{itemize}
-      \item Provide more details
-      \begin{itemize}
-            \item why does the git project not work?
-            \item overall architecture
-            \item how does the script work?
-            \item folder structure
-            \item configuration
-      \end{itemize}
-\end{itemize}
+To check how the HDR+ image processing pipeline described by Hasinoff et al. (2016) \cite{Hasinoff2016burst}
+handles scenes under different lighting
+conditions, an implementation of the pipeline should be made to work and applied to
+different image bursts. The implementation used was developed by Timothy Brooks
+\cite{Brooks2016git} and published as open source project.
 
-\cite{Brooks2016git} has implemented the image processing pipeline described in \cref{sec:related_work}. To do this, 
-he uses Halide, a programming language embedded in C++ that allows efficient image processing 
-pipelines to be implemented with little effort. Halide itself requires LLVM to compile. 
-Unfortunately, the project has not been actively maintained for quite some time and 
-since new versions of Halide and LLVM have been released in the meantime, some of which were 
-not backwards compatible, the project could not be compiled out of the box. After many hours of 
-trial and error, the project was able to compile with version 10 of both Halide and LLVM. 
-To get a reproducible executable version of \cite{Brooks2016git}, a Docker image was created that 
-contains the application and runs it on container startup. To improve efficiency, a script was created 
-that starts processing all image bursts that are stored inside a bursts directory, which is shared
-with the Docker container, in parallel. \Cref{fig:architecture} shows the architecture described above.
+\subsection{Difficulties in getting the project to work}
+\label{sec:difficulties}
+
+Unfortunately, the project did neither compile out of the box 
+nor was it well documented because it was not maintained for quite some time, so I 
+needed to research which dependencies are needed to compile it.
+
+It was documented that the implementation uses Halide \cite{halide2022}, which is a programming language
+embedded in C++ that provides a higher level API to efficiently manipulate images. Halide
+itself relies on LLVM \cite{llvm2022}. But the project does not compile with the current version
+of Halide, which is version 14 at the time of writing. There was a git commit message
+that explicitly mentions Halide version 10. Halide version 10 itself did not compile with
+the current version of LLVM, which is version 14 at the time of writing. Instead it needs
+LLVM version 10. Unfortunately, the operating system I was using, Ubuntu 22.10 \cite{ubuntu2022}, 
+does not have that LLVM version in its package repository so I had to compile it myself, which took
+quite some time.
+
+\subsection{Making the project platform independent}
+\label{sec:resolving}
+
+Since it is not user-friendly to compile the project and all its dependencies by hand and thus it 
+is also difficult to write a universal manual for different operating systems, the idea came up to 
+make it platform independent by means of containerization. Docker was chosen as the containerization 
+technology because of its prevalence and acceptance.
+
+In a multi-step build process, a Docker image based on Ubuntu 20.10. is created that contains the 
+executable HDR+ implementation and runs it on container startup. The resulting Docker image is 
+456 MB in size and can be made available via image registries without users having to compile themselves.
+
+\subsection{Processing multiple bursts in parallel}
+\label{sec:parallel}
+
+Since the implementation is designed to process only one image burst, there is a large overhead 
+due to the necessary starting and stopping of a container. To address this issue, a shell script 
+was created that starts an image processing pipeline for each image burst in a bursts directory 
+shared between the operating system and the container when the container is started. Since the 
+implementation accepts start parameters to adjust the amount of gain and dynamic range compressen 
+applied when processing a burst, these can be set in a configuration 
+file for the burst. \Cref{fig:architecture} illustrates the architecture described beforehand. 
+The start parameters as well as the output of the processing pipeline are saved 
+in a log file, which is stored in the respective burst directory just like the result image.
+To avoid reprocessing the same image burst over and over again, all individual burst folders containing 
+a result image with default name are excluded from processing.
 
@@
 \section{Experiments}
-\label{sec:Experiments}
+\label{sec:experiments}
 
-\begin{itemize}
-      \item Insert images
-      \item Compare raw vs processed
-      \item Show examples for scenarios:
-      \begin{itemize}
-            \item Low light noise reduction
-            \item Improving contrast / dynamic range
-            \item Improving overall colors
-      \end{itemize}
-      \item Show fails
-\end{itemize}
+To check how reliably the HDR+ implementation delivers good results, 
+several image bursts from different scenes were processed. The results 
+are presented in the following sections.
 
-\subsection{Noisy low light situations}
+\subsection{Low light situations}
+\label{lowlight}
+
+As a first test of the pipeline, several images of a dried flower 
+were taken in a poorly lit room in the evening. To get even darker 
+raw images, shutter speed and ISO were intentionally set lower than 
+would be appropriate for the lighting situation. After the burst was
+processed by the HDR+ implementation, a pleasing result came out. 
+In \Cref{fig:teaser}, an excerpt of the burst is compared to the result.
+
+\subsection{Images with high noise}
+\label{sec:noise}
 
@@
 
-To find out how the HDR+ implementation handles images containing high noise, several 
-image bursts with high noise were processed. As can be seen in \cref{fig:noise}, the noise was 
+To check how well the HDR+ implementation is able to handle image bursts that have high noise, several 
+images were processed. The scenes that were checked show objects and people inside enclosed 
+spaces as well as a city at night. As can be seen in \Cref{fig:noise}, the noise was 
 removed very well in all examples. Even when zooming in, hardly any noise is visible 
-compared to the original image.  The results were all obtained with the same starting 
-parameters and were satisfactory throughout.
+compared to the original image. The results were all obtained using same starting 
+parameters gain $g=1.0$ and dynamic range compression $c=2.5$ and were satisfactory throughout.
 
 \subsection{Low contrast or dynamic range situations}
+\label{sec:contrast}
 
@@
 
-\cref{fig:contrast}
+Various image bursts were processed where the raw images were very pale 
+and low in contrast. After processing, good results were obtained, showing 
+a high dynamic range. \Cref{fig:contrast} compares a sample image from the image burst 
+with the processed result, showing the difference in dynamic range. While 
+increasing the dynamic range is basically well possible, individual parameters 
+per image have to be tried out here compared to the experiments in \cref{sec:noise}, 
+which depend on the respective lighting situation. Thus, a too high gain 
+parameter can quickly lead to an overexposed and a too high dynamic range 
+compression parameter to a comic-like looking result image.
 
 \subsection{Moving objects}
+\label{sec:moving}
 
@@
       \centering
-      \caption{Low light image capture of moving objects}
+      \caption{
+            Left images: Sample from a image burst captured with a Sony Alpha A6000 camera
+            with focal length $18mm$, shutter speed $1/100s$, ISO $680$ 
+            and aperture $f/4.0$ in a low light situation with moving cars.
+            Right image: Processed image burst with settings gain $g = 1.6$ and dynamic 
+            range compression $c = 3.0$. Ghosting is clearly visible when looking at the 
+            fast moving white car in the bottom but not when looking at the slower cars
+            in the top.
+      }
       \label{fig:moving}
@@
 
-\begin{figure}
-      \hspace{\fill}
-      \includegraphics[width=0.9\linewidth]{images/ghosting.png}
-      \hspace{\fill}
-      \centering
-      \caption{Detail of \cref{fig:moving} showing ghosting }
-      \label{fig:ghosting}
-\end{figure}
-
-\cref{fig:moving}
-\cref{fig:ghosting}
+While small movements could be processed well, it should be investigated how to 
+process fast moving objects over a long distance. For this purpose, an image burst 
+of a road with moving cars at night was recorded, which is shown in \cref{fig:moving}. 
+Although the low light situation was basically processed satisfactorily and not 
+too fast cars could be aligned well, clear ghosting artifacts can be seen in the 
+for the very fast moving white car.
 
@@
 \section{Conclusions}
-
-\begin{itemize}
-      \item Are there scenes that are very easy or hard to improve?
-      \item Advantages:
-      \begin{itemize}
-            \item (Revived dead open source project, yay)
-            \item Portable solution because Docker
-            \item Parallel processing of multiple bursts
-            \item Not as much work as manually editing bracketed bursts in photoshop
-      \end{itemize}
-      \item Drawbacks:
-      \begin{itemize}
-            \item Long initial compiling time when building Docker image
-            \item Overhead because Docker
-            \item Ease of use: command-line only, adjusting config by editing a file
-      \end{itemize}
-      \item Future:
-      \begin{itemize}
-            \item Use case: Photographer wanting HDR images, but does not want to spend
-                  hours in photoshop
-            \item Providing GUI:
-            \begin{itemize}
-                  \item Hide docker and script execution for non-nerdy users
-                  \item Select burst folders to processes
-                  \item Adjust gain and compress parameters by slider per folder
-                  \item Start processing of selected folders via button click
-                  \item Show result images when finished
-            \end{itemize}
-      \end{itemize}
-\end{itemize}
 \label{sec:conclusion}
 
-%-------------------------------------------------------------------------
-\section{Acknowledgements}
-\label{sec:acknowledgements}
-\begin{itemize}
-      \item Cat
-      \item Elementary school teacher5
-      \item Random dude at the bar who bought a round
-\end{itemize}
+By containerizing Brooks' \cite{Brooks2016git} open source project, it is possible 
+to process multiple raw image bursts simultaneously with the HDR+ 
+image processing pipeline, independent of the host operating system. Users no 
+longer need to compile the application themselves and worry about dependencies, 
+but could simply pull the Docker image from an image repository.
+
+The results obtained from the experiments in \cref{sec:experiments} were consistently 
+satisfactory. The only challenge found is the processing of fast moving objects, as 
+ghosting effects can easily occur here. However, to achieve good results, the start parameters must be configured depending 
+on the lighting situation. Since the individual configuration file of a burst must 
+be adapted for this purpose, it can become tedious for the user to want to process
+many bursts with different lighting situations in parallel, since similar lighting 
+conditions often require similar parameters.
+
+One disadvantage of the approach followed is that running inside a container creates 
+some overhead because the container must be started first and only the CPU is used 
+to process the images by default. As a result, processing a single burst takes several seconds
+depending on size and amount of the input images, which precludes its use in time-critical scenarios. 
+It should be examined whether this is due to the specific implementation or whether the performance 
+can be improved significantly by using tools that offer GPU support in container environments 
+like NVIDIA container toolkit \cite{nvidia2015docker}.
 

### 2023-02-09 documentation/paper.tex
Finish

@@
 
-\subsection{Images with high noise}
-\label{sec:noise}
-
-\begin{figure}
-      \hspace{\fill}
-      \includegraphics[width=0.9\linewidth]{images/noise.png}
-      \hspace{\fill}
-      \centering
-      \caption{
-            Left images: Noisy low light sample from bursts provided by the supplemental dataset
-            to \cite{Hasinoff2016burst}. Top row shows full image while bottom shows zoom in noisy
-            area.
-            Right images: Processed burst images with settings gain $g=1.0$ and dynamic 
-            range compression $c=2.5$.
-      }
-      \label{fig:noise}
-\end{figure}
-
-To check how well the HDR+ implementation is able to handle image bursts that have high noise, several 
-images were processed. The scenes that were checked show objects and people inside enclosed 
-spaces as well as a city at night. As can be seen in \Cref{fig:noise}, the noise was 
-removed very well in all examples. Even when zooming in, hardly any noise is visible 
-compared to the original image. The results were all obtained using same starting 
-parameters gain $g=1.0$ and dynamic range compression $c=2.5$ and were satisfactory throughout.
-
 \subsection{Low contrast or dynamic range situations}
@@
 
+\subsection{Images with high noise}
+\label{sec:noise}
+
+\begin{figure}
+      \hspace{\fill}
+      \includegraphics[width=0.8\linewidth]{images/noise.png}
+      \hspace{\fill}
+      \centering
+      \caption{
+            Left images: Noisy low light sample from bursts provided by the supplemental dataset
+            to \cite{Hasinoff2016burst}. Top row shows full image while bottom shows zoom in noisy
+            area.
+            Right images: Processed burst images with settings gain $g=1.0$ and dynamic 
+            range compression $c=2.5$.
+      }
+      \label{fig:noise}
+\end{figure}
+
+To check how well the HDR+ implementation is able to handle image bursts that have high noise, several 
+images were processed. The scenes that were checked show objects and people inside enclosed 
+spaces as well as a city at night. As can be seen in \Cref{fig:noise}, the noise was 
+removed very well in all examples. Even when zooming in, hardly any noise is visible 
+compared to the original image. The results were all obtained using same starting 
+parameters gain $g=1.0$ and dynamic range compression $c=2.5$ and were satisfactory throughout.
+
 \subsection{Moving objects}
@@
 process fast moving objects over a long distance. For this purpose, an image burst 
-of a road with moving cars at night was recorded, which is shown in \cref{fig:moving}. 
+of a road with moving cars at night was recorded, which is shown in \Cref{fig:moving}. 
 Although the low light situation was basically processed satisfactorily and not 
@@
 
+In a next step, the results could be compared with those of a more up-to-date burst processing 
+pipeline in terms of image quality and performance. A suitable candidate would be the neural 
+network-based approach presented by Dudhane et al. (2022) \cite{Dudhane2022restoration}, 
+as the individual steps of this pipeline are fundamentally different from those of the 
+HDR+ pipeline and the authors make their source code available in an open source project
+\cite{Dudhane2022git}.
+
 %-------------------------------------------------------------------------

### 2023-02-09 documentation/paper.tex
Finish

@@
 
+\subsection{Creating HDR images via exposure bracketing}
+\label{sec:bracketing}
+
 One way that burst photography and HDR techniques can be used together
@@
 
+\subsection{Challenges of photography with mobile devices}
+\label{sec:challenges}
+
 According to the photo sharing community Flickr, the most 
@@
           to DSLR or mirrorless cameras, which can result in lower sensitivity 
-          to light. This can make it difficult to capture usable images in low l
-          ight conditions without using long exposures or high ISO values, 
+          to light. This can make it difficult to capture usable images in low 
+          light conditions without using long exposures or high ISO values, 
           which can introduce noise and other artifacts.
@@
 
-To address these constraints, several techniques can be used to improve the performance 
-of mobile cameras in low light conditions. These include:
+\subsection{Addressing these challenges}
+To address the constraints mentioned in \cref{sec:challenges}, several techniques 
+from computational photography can be used to improve the quality of images captured 
+captured mobile cameras \cite{delbracio2021mobile}. These include:
 
@@
     \item Noise reduction: Noise reduction algorithms can be used to reduce the noise 
-          introduced by high ISO values or long exposures. These algorithms can smooth 
+          introduced by high ISO values. These algorithms can smooth 
           out the image while preserving edges and other important details.
 
-    \item High dynamic range techniques: HDR techniques, such as burst photography 
-          and computational photography, can be used to extend the dynamic range of mobile 
+    \item High dynamic range techniques: HDR techniques, such as burst photography, can be used to extend the dynamic range of mobile 
           cameras and capture more detail in both the shadow and highlight areas of an image.
@@
 
+\subsection{HDR+ burst processing pipeline}
+\label{sec:hdrpluspipeline}
 The HDR+ image processing pipeline is a computational photography technique developed by Google for use 
@@
 
+\subsection{Improvements and new approaches since HDR+}
+\label{sec:newerstuff}
+
 To increase the amount of light collected, Levoy {\&} Pritch (2018) \cite{levoy2018psl} describe 
@@
 
-To check how the HDR+ image processing pipeline described by Hasinoff et al. (2016) \cite{Hasinoff2016burst}
+To check how the HDR+ image processing pipeline described in \cref{sec:hdrpluspipeline}
 handles scenes under different lighting

### 2023-02-09 documentation/paper.tex
Finish

@@
 suffer from constructional limitations that restrict image quality, such as smaller 
-sensors and pixels, shorter focal lengths and smaller apertures. To compensate for 
+sensors and pixels, shorter focal lengths as well as smaller apertures. To compensate for 
 these limitations, techniques from computational photography are used, whereby many 
@@
 
-\subsection{Moving objects}
-\label{sec:moving}
-
 \begin{figure*}
@@
 \end{figure*}
+
+\subsection{Moving objects}
+\label{sec:moving}
 
